---
title: "Metadata"
format: html
---

## Load libraries

```{r}
#| label: load-libraries
#| include: true
#| warning: false
library(dplyr)
library(tidyr)
library(readr)
library(lubridate)
library(sf)
library(tmap)
library(DT)

# Set tmap mode and basemap
tmap_mode("view")
tmap_options(basemap.server = c("OpenStreetMap", "Esri.WorldImagery"))

# Set timezone to NZST
withr::local_locale(c("LC_TIME" = "C"))
withr::local_timezone("Etc/GMT-12")

# Load functions
# source("R/qc_funs.R")

```

## Get data from GitHub

```{r}
#| label: download-data
#| cache: true
piggyback::pb_download(
  file = "rotoehu_data.zip",
  dest = ".",
  repo = "limnotrack/f_rotoehu",
  tag = "v0.0.1"
)

# Unzip the file
unzip("rotoehu_data.zip")
list.files("rotoehu_data", recursive = TRUE)

```

## Files

```{r}
#| label: files
#| echo: false

files <- list.files("rotoehu_data", recursive = TRUE)
data.frame(
  File = files,
  Description = NA
) |> 
  mutate(
    Description = case_when(
      File == "device_position.csv" ~ "Device position",
      File == "device_variable.csv" ~ "Device variable relationship",
      File == "qc_filters.csv" ~ "Quality control filters",
      File == "sensor_calibrations.csv" ~ "Sensor calibrations",
      File == "rotoehu_qc.csv" ~ "Quality controlled data",
      File == "sensor_reference.csv" ~ "Sensor reference measurements",
      File == "sensor_scaling.csv" ~ "Sensor scaling relationships",
      File == "site_devices.csv" ~ "Mapping of devices to sites",
      File == "site_events.csv" ~ "Site events",
      File == "sites.csv" ~ "Site metadata",
      File == "variables.csv" ~ "Variable description"
    )
  ) |> 
  datatable(
    options = list(
      pageLength = 15,
      dom = "t"
    ), rownames = FALSE
  ) 

```



## Device position

The device position is stored in a CSV file. The file contains the following columns:
- `device_id`: The unique identifier for the device.
- `reference`: The location of the device. This can be depth ("d"), height ("h")
or elevation ("e").
- `z_relative`: The relative position of the device in meters. This is the distance
from the reference point to the device.

```{r}
#| label: device-position

device_position <- read_csv("rotoehu_data/device_position.csv", col_types = cols())

device_position |> 
  datatable(
    options = list(
      pageLength = 5,
      lengthMenu = c(5, 10, 20),
      scrollX = TRUE,
      dom = "t"
    ), rownames = FALSE
  ) 

```

## Device variable

The device variable is stored in a CSV file. The file contains the following columns:
- `device_id`: The unique identifier for the device.
- `var_abbr`: The variable abbreviation. This is the short name for the variable.

```{r}
#| label: device-variable

device_variable <- read_csv("rotoehu_data/device_variable.csv", col_types = cols())
device_variable |> 
  datatable(
    options = list(
      pageLength = 5,
      lengthMenu = c(5, 10, 20),
      scrollX = TRUE,
      dom = "t"
    ), rownames = FALSE
  ) 
```

## Quality control filters

The quality control filters are stored in a CSV file. The file contains the following columns:
- `var_abbr`: The variable abbreviation. This is the short name for the variable.
- `low`: The lower limit for the variable. This is the minimum value for the variable.
- `high`: The upper limit for the variable. This is the maximum value for the variable.
- `roc`: The rate of change for the variable. This is the maximum rate of change for the variable.
- `consec`: The consecutive number of points for the variable. This is the minimum number of consecutive points for the variable.
- `interp`: The interpolation for the variable. This is the maximum number of points for the variable.

```{r}
#| label: qc-filters

qc_filters <- read_csv("rotoehu_data/qc_filters.csv", col_types = cols())

qc_filters |> 
  datatable(
    options = list(
      pageLength = 5,
      lengthMenu = c(5, 10, 20),
      scrollX = TRUE,
      dom = "t"
    ), rownames = FALSE
  )

```

## Quality controlled data

This is the finished quality controlled data. There is a summary of this
data on the [Quality control page](rotoehu-qc-summary.html). 

## Sensor calibrations

The sensor calibrations are stored in a CSV file. The file contains the following columns:
- `device_id`: The unique identifier for the device.
- `date`: The date of the calibration.
- `site`: The site of the calibration.
- `variable`: The variable of the calibration.
- `temperature`: The temperature of the calibration.
- `type`: The type of calibration.
- `comment`: The comment for the calibration.

```{r}
#| label: sensor-calibrations

sensor_calibrations <- read_csv("rotoehu_data/sensor_calibrations.csv", col_types = cols())

sensor_calibrations |> 
  datatable(
    options = list(
      pageLength = 5,
      lengthMenu = c(5, 10, 20),
      scrollX = TRUE
    ), rownames = FALSE
  )

```

## Sensor reference

The sensor reference is stored in a CSV file. The file contains the following columns:
- `device_id`: The unique identifier for the device.
- `date`: The date of the reference measurement.
- `reference_type`: The type of reference measurement.
- `value_actual`: The actual value of the reference measurement.
- `units_value`: The units of the actual value.
- `value_measured`: The measured value of the reference measurement.
- `units_sensor`: The units of the measured value.
- `temperature`: The temperature of the reference measurement.
- `comment`: The comment for the reference measurement.

```{r}
#| label: sensor-reference

sensor_reference <- read_csv("rotoehu_data/sensor_reference.csv", col_types = cols())

sensor_reference |> 
  datatable(
    options = list(
      pageLength = 5,
      lengthMenu = c(5, 10, 20),
      scrollX = TRUE
    ), rownames = FALSE
  )
```

## Sensor scaling

The sensor scaling is stored in a CSV file. The file contains the following columns:
- `device_id`: The unique identifier for the device.
- `date`: The date of the scaling.
- `offset`: The offset for the scaling.
- `multiplier`: The multiplier for the scaling.
- `range`: The range for the scaling.
- `log_multiplier`: The logger multiplier for the scaling.
- `source`: The source of the scaling factors.
- `comment`: The comment for the scaling.

```{r}
#| label: sensor-scaling

sensor_scaling <- read_csv("rotoehu_data/sensor_scaling.csv", col_types = cols())

sensor_scaling |> 
  datatable(
    options = list(
      pageLength = 5,
      lengthMenu = c(5, 10, 20),
      scrollX = TRUE
    ), rownames = FALSE
  )
```

## Site devices

The site devices are stored in a CSV file. The file contains the following columns:
- `site`: The site of the device.
- `device_id`: The unique identifier for the device.
- `date_from`: The date the device was installed.
- `date_to`: The date the device was removed.
- `notes_device`: The notes for the device.
- `notes`: The notes for the site.

```{r}
#| label: site-devices

site_devices <- read_csv("rotoehu_data/site_devices.csv", col_types = cols())

site_devices |> 
  datatable(
    options = list(
      pageLength = 5,
      lengthMenu = c(5, 10, 20),
      scrollX = TRUE
    ), rownames = FALSE
  )

```

## Site events

The site events are stored in a CSV file. The file contains the following columns:
- `site`: The site of the event.
- `date`: The date of the event.
- `site_visit`: Was the site visited?
- `variables`: The variables of the event.
- `action`: The action of the event. Can be "deployed", "removed", "cleaned", 
"rebooted" or "other".
- `comment`: The comment for the event.

```{r}
#| label: site-events

site_events <- read_csv("rotoehu_data/site_events.csv", col_types = cols())

site_events |> 
  datatable(
    options = list(
      pageLength = 5,
      lengthMenu = c(5, 10, 20),
      scrollX = TRUE
    ), rownames = FALSE
  )

```

## Sites

The sites are stored in a CSV file. The file contains the following columns:
- `site`: The site of the device.
- `location`: The location of the site.
- `type`: The type of site. Can be "lake", "river" or "other".
- `customer`: The customer of the site.
- `lon`: The longitude of the site.
- `lat`: The latitude of the site.
- `elev`: The elevation of the site.

```{r}
#| label: sites

sites <- read_csv("rotoehu_data/sites.csv", col_types = cols())

sites |> 
  mutate(lon = round(lon, 2), lat = round(lat, 2)) |>
  datatable(
    options = list(
      pageLength = 5,
      lengthMenu = c(5, 10, 20),
      scrollX = TRUE
    ), rownames = FALSE
  )

```
## Variables

The variables are stored in a CSV file. The file contains the following columns:

- `var_abbr`: The variable abbreviation. This is the short name for the variable.
- `full_text`: The full text of the variable. This is the long name for the variable.
- `parsed`: The parsed name of the variable. This is the name used for plotting.
- `label`: The label of the variable. This is the name used for the legend.

```{r}
#| label: variables

variables <- read_csv("rotoehu_data/variables.csv", col_types = cols())

variables |> 
  datatable(
    options = list(
      pageLength = 5,
      lengthMenu = c(5, 10, 20),
      scrollX = TRUE
    ), rownames = FALSE
  )
```


